---
title: "Vignette for the advRlab4package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"Vignette for the advRlab4package"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# The advRlab4package
The purpose of this package is to aid a user in performing a simple regression analysis. To this end, the package features and RC class named "linreg" which is equipped with various methods that are available to the user. Let's begin by loading the package.

```{r setup}
library(advRlab4package)
```

# The linreg class
In order to use the `linreg` class, an instance of the `linreg` class must be created. This instance is an object that has inherited all it's fields (variables) and methods (functions) from the `linreg` class. To illustrate this, consider how the class/group of all dogs (consisting of methods such as `jump()` , `run()` and `fetch()`) relate to an individual dog, Fluffy. An instance of the linreg class can easily be created like displayed in the chunk below. The two required arguments are a [formula class object](https://towardsdatascience.com/r-formula-tutorial-for-beginners-1a6d88e2d0bb), and a dataframe. In the example below, we will specify that we wish to analyse the iris dataset, and that we wish to model Petal length as a function of Sepal width. When the linreg instance is created, all the associated mathematical operations are carried out. The results of the analysis can then be extracted with the other methods in the `linreg` class.

```{r}
# Creating an instance of the linreg class
linreg_instance <- linreg$new(formula = Petal.Length ~ Sepal.Width, data = iris)
```


## The `linreg` `plot()` method
The plot method works like this.

```{r}
# Call the plot method of our linreg object instance `linreg_instance`
linreg_instance$plot()
```

ggplot2 is data visualization package.Its "grammar of graphics".There are three sub parts.
data - The dataset with observations to be visualized (data.frame)
geom -  The geometric representation of data
aes - The mapping of colors/shape to data

```{r}
# Load the ggplot2 package
# library(ggplot2)
# 
# p1 <- ggplot ( data = iris ) +
#       aes(x=years , y= level ) +
#       geom_point ()

# Apply the theme function on the ggplot object
#theme(p1)
```

# The `theme()` function
The theme applies some things/changes onto a ggplot object. Here is an example. As you can see, the theme provides *some* kind of changes to the ggplot object.

```{r}
#use ggtheme import
# theme_economist()

```


## Some other `linreg` methods
They work like this.

```{r}
# linreg_instance$resid()
# linreg_instance$pred()
# linreg_instance$coef()
# linreg_instance$summary()

```

Reference Classes (RC), RC methods belong to objects, not functions.
In this code, define a Reference Class "linreg".


Call a method on the instance: 
EX : class_name$methods_name()


Testing or Show result 
```{r eval=FALSE}
# linob <- linreg$new(formula = Species ~ Petal.Length + Petal.Width + Sepal.Length + Sepal.Width, data=iris |> dplyr::mutate(Species = as.numeric(Species)))
# plot(linob)
```

