---
title: "Vignette for the advRlab4package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"Vignette for the advRlab4package"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(advRlab4package)
#library(ggplot2)
```

```{r}
theme()
```


# The linreg class
An instance of the linreg class can easily be created like displayed in the chunk below. The two required arguments are a formula class object, and a dataframe.

```{r}
# Example
linreg_instance <- linreg$new(formula = Petal.Length ~ Sepal.Width,
                          data = iris)
```


## The `linreg` `plot()` method
The plot method works like this.

```{r}
# Call the plot method of our linreg object instance `linreg_instance`
linreg_instance$plot()
```


## Some other `linreg` methods
They work like this.

```{r}

```


# The `theme()` function
The theme applies some things/changes onto a ggplot object. Here is an example. As you can see, the theme provides *some* kind of changes to the ggplot object.

```{r}
# Create a ggplot object
gg_object <- ggplot(data=iris) |> geom_point(aes(x=Petal.Length, y=Petal.Width))

# Apply the theme function on the ggplot object
theme(gg_object)
```




# Extra things (maybe remove, or merge into the rest of the vignette)

Reference Classes (RC), RC methods belong to objects, not functions.
In this code, define a Reference Class "linreg" with data fields (formula,data,x,y,coefficients_beta,res_var_sigma2,..) and method (summary).


Call a method on the instance: 
EX : class_name$methods_name()


Testing or Show result 
```{r eval=FALSE}
linob <- linreg$new(formula = Species ~ Petal.Length + Petal.Width + Sepal.Length + Sepal.Width, data=iris |> dplyr::mutate(Species = as.numeric(Species)))
plot(linob)
```

