---
title: "Vignette for the advRlab4package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"Vignette for the advRlab4package"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package to handle Linear Regression models.
```{r setup}
library(advRlab4package)
```


# The linreg class
An instance of the linreg class can easily be created like displayed in the chunk below. The two required arguments are a formula class object, and a dataframe.

```{r}
# Example
linreg_instance <- linreg$new(formula = Petal.Length ~ Sepal.Width,
                          data = iris)
```


## The `linreg` `plot()` method
The plot method works like this.

```{r}
# Call the plot method of our linreg object instance `linreg_instance`
linreg_instance$plot()
```

ggplot2 is data visualization package.Its "grammar of graphics".There are three sub parts.
data - The dataset with observations to be visualized (data.frame)
geom -  The geometric representation of data
aes - The mapping of colors/shape to data

```{r}
# Load the ggplot2 package
library(ggplot2)

gg_object <- ggplot ( data = iris ) +
      aes(x=years , y= level ) +
      geom_point ()

# Apply the theme function on the ggplot object
theme(gg_object)
```

# The `theme()` function
The theme applies some things/changes onto a ggplot object. Here is an example. As you can see, the theme provides *some* kind of changes to the ggplot object.

```{r}
theme(panel.grid.major = ggplot2::element_blank(),
      panel.grid.minor = ggplot2::element_blank(),
      plot.title = ggplot2::element_text(hjust = 0.5)
      )

```


## Some other `linreg` methods
They work like this.

```{r}
linreg_instance$resid()
linreg_instance$pred()
linreg_instance$coef()
linreg_instance$summary()

```

Linear Algebra calculation example Here .
^y = Xβ^

```{r}
#Example :
# Use solve() or inv(). solve() seems to keep the row and col labels.
  coefficients_beta <<- solve(t(X) %*% X) %*% t(X) %*% y

  fitted_y <<- X %*% coefficients_beta
  data$fitted_y <<- fitted_y
```

PRED method use for fitted_y and return output.Example is here 
```{r}
# --- PRED method ---
linreg$methods(pred = function(){
  return(fitted_y)})
```


Reference Classes (RC), RC methods belong to objects, not functions.
In this code, define a Reference Class "linreg".


Call a method on the instance: 
EX : class_name$methods_name()


Testing or Show result 
```{r eval=FALSE}
# linob <- linreg$new(formula = Species ~ Petal.Length + Petal.Width + Sepal.Length + Sepal.Width, data=iris |> dplyr::mutate(Species = as.numeric(Species)))
# plot(linob)
```

